---
title: "1_AnalysisRaster"
author: "Jojo"
date: "6 March 2016"
output: html_document
---

Lecture 5: Read in raster data using R

```{r}
library(raster)
setwd("F:\\R_asGIS\\1ANALYSIS")
band1=raster("band1.tif")
band1

band3=raster("band3.tif")
band3

band4=raster("band4.tif")
band4

plot(band1)

band2=raster("band2.img")
band2

b3=raster("CA2015_new.rst")
writeRaster(b3,"ConvertToTif.tif",overwrite=TRUE) 

setwd("F:\\R_asGIS\\1ANALYSIS\\bands")

rlist=list.files(pattern="tif$", full.names=TRUE) 
# CREATE RASTER STACK
rasters = stack(rlist)

#Examine your raster stack
names(rasters)
rasters
plot(rasters)


```

Lecture 6: Examine and Modify CRS of a raster band

```{r}
setwd("F:\\R_asGIS\\1ANALYSIS")
band1

b1LL <- projectRaster(band1, crs='+proj=longlat')
b1LL
plot(b1LL)



#lat long to utm

x=" +proj=utm +zone=48 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"

b1U=projectRaster(b1LL,crs=x)
b1U

```

Lecture 7: Modify raster stack

```{r}
band1=raster("band1.tif")
band1

band3=raster("band3.tif")
band3

band4=raster("band4.tif")
band4

stackR=stack(band1,band3,band4)
plot(stackR)

bR=brick(band1,band3,band4)
bR

plot(stackR$band1)

setwd("F:\\R_asGIS\\1ANALYSIS\\bands")

rlist=list.files(pattern="tif$", full.names=TRUE) 
# CREATE RASTER STACK
rasters = stack(rlist)

rasters

#Drop layers: from a given stack, specify the index of the layer to be dropped
#in this case, drop the 6th layer
rastersD1=dropLayer(rasters,6)
names(rastersD1)

rastersD2=dropLayer(rasters,c(1,6))#specify indices 1 and 6

rastAdd=addLayer(rastersD2,band1) #add b1 to the stack

```

Lecture 8: Plot RGB Composites

```{r}
rasters #please read in all 6 Landsat bands

plotRGB(rasters,r=3,g=2,b=1, stretch = "hist")

plotRGB(rasters,r=3,g=2,b=1, scale=800, stretch = "Lin")

plotRGB(rasters,r=4,g=3,b=2, stretch = "hist")

```

Lecture 9a: Band arithmetic on raster data

```{r}
rasters

s=calc(rasters,sum) #will sum up all raster bands

func <- function(x) ##apply a custom function to your stack
{ 
  x[x<300] <- NA 
  return(x) 
}
rc2 <- calc(s, func)

s2=s[s<300]<-NA 

# (NIR-Red)/(NIR+Red)

ndvi=(rasters$band4-rasters$band3)/(rasters$band3+rasters$band4) 
plot(ndvi) #0 to 1

```

Lecture 10: RECLASSIFY: BUILD A CATEGORICAL MAP

```{r}
m <- c(-0.2, 0.2, 1,  0.2, 0.6, 2,  0.6,1, 3)
mat <- matrix(m, ncol=3, byrow=TRUE) #matrix of categorical value classes 

rc <- reclassify(ndvi, mat)
plot(rc)

```

Lecture 11: Calculate  % land cover of categorical maps

```{r}
library(SDMTools)

#our reclassified raster is in UTM. For SDMTools we need it in lat long

#rc2 <- projectRaster(rc, crs='+proj=longlat')

#c=ClassStat(rc, cellsize = 30, latlon = FALSE)

```

Lecture 13: Resampling rasters

```{r}
setwd("F:\\R_asGIS\\1ANALYSIS")
h=raster("tamd_hill.tif")
n=raster("tamd_ndvi.tif")

plot(n)
nLL <- projectRaster(n, crs='+proj=longlat')

n2=resample(nLL,h,"ngb")


```

Lecture 14: Clipping Rasters in R

```{r}
library(raster)
hill=raster("1hillshade.tif")
plot(hill)

e <- extent(105.6, 105.7, 20.5, 21.5) # longitude, latitude

abs=crop(hill,e2)
plot(abs)

e2=drawExtent()#-- this is a dynamic clipping tools. It has been #
#for compilation

library(rgdal)
tdao=readOGR(".","VietnamPA_name__Tam Dao")
plot(tdao,add=T)

A=mask(hill,tdao)
plot(A)

pa1=readOGR(".","VietnamPA")
plot(pa1,add=T)
dat <- extract(hill, pa1,fun=mean, na.rm=TRUE)
head(dat)


```

Lecture 16: Topographic Calculations in R

```{r}
#1)Read in raster of digital elevation model (DEM) already stored on hard drive 
dem=raster("vie_dem_srtm.tif")#elevation in m

#2)Download elevation data from internet
#country code: http://max2.ese.u-psud.fr/epc/conservation/Girondot/Publications/Blog_r/Entrees/2014/11/2_Other_geographic_databases.html
dem2 = getData("alt", country = "VNM") #you can calculate slope etc from these

#4)Plot areas of a certain value of elevation
plot(dem, zlim=c(1000,3000),main="Elevation 1000m-3000m") #areas where elevation is between 1000m-3000m

slope=terrain(dem,opt="slope",unit="degrees")#calc slope in degrees
aspect=terrain(dem,opt="aspect")

x <- terrain(dem, opt = c("slope", "aspect"), unit = "degrees") #plot slope and aspect in degrees
plot(x)

hill <- hillShade(slope, aspect, 40, 270)#hilshade
plot(hill)


```

